\section*{|| Technical skills ||}
\begin{itemize}
	\item I have been programming in C and C++ for over 4 years professionally and \number\numexpr\year-2018\relax~years on my spare time as an enthuastic hobby programmer. I aim for simplicity, safety and speed when programming. Fairly good understanding of assembly language (x86-64). Thorough experience integrating and using libraries, such as LLVM, GLFW, Dear ImGUI, STB single-header libraries, sokol, meshoptimizer, Volk, Raylib, Qt, Expat, JSMN...
	
	\item Comfortable with systems programming, both Windows and POSIX systems.
	
	\item Passionate about data-oriented programming, emphasizing a deep understanding of both the platform and data to develop effective solutions. Strong interest in computer architecture and hardware optimization to maximize performance. Well-versed in object-oriented design, with professional experience applying both object-oriented and data-oriented paradigms in software development.
	
	\item Personal experience in compiler engineering, developing several toy programming languages as a passion project with a focus on minimizing dependencies, maintaining code ownership, and optimizing compile times. My current compiler project has successfully self-hosted. Open source contributions to compiler projects, such as LLVM, Zig or C3.
	
	\item Passion for SIMD instruction sets, especially AVX-512. I try to spend time learning how to properly vectorize my code and maximize throughput.
	
	\item Very brief personal experience with low-level graphics APIs, such as Vulkan, OpenGL and DirectX (11, 12), having practiced more with the open-source ones. Fairly good understanding of game engines and the GPU pipeline.
	
	\item Fairly in-depth understanding of how an operating system kernel works, performance constraints and hardware-software interaction details. Developed some operating system kernels from scratch with very primitive functionality.
	
	\item Expertise working with files, parsing and generating them, both text and binary formats.
	
	\item Language interoperability based on the C ABI. Binding creation to interoperate between C, C++, Objective-C, Rust and Zig. More than decent understanding of how linkers work.
	
	\item API design and project organization.
	
	\item Use of build systems like CMake, Ninja, MSBuild, Makefile, Zig Build, Maven and Ant, both professionally and personally.
	
	\item Use of version control systems such as Git, Perforce or CVS, both professionally and personally.
	
	\item Experienced with both shell environments (Windows Batch, Unix Bash) and graphical development environments (Visual Studio, JetBrains IDEs).
	
	\item Experience with other programming languages, like Zig, Java, Rust and Python.
\end{itemize}